DM: A Distributed Decision Making Model for \\ Dynamic Formation of Web services Communities

### 2014-12-06 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Now, we evaluate the performance of the strategy profiles generated for our training set for other communities or the evaluation set. We create one thousand communities out of the web services in the data set that were not involved in the training set. We define a distance function that measures the difference between basic features of communities.

>>>>

Now, we evaluate the performance of the strategy profiles generated based on our data set for other communities which are not included in the decision tree creation process. We create one thousand communities out of the web services in the data set that were not involved in the decision model creation process. We define a distance function that measures the difference between basic features of communities.
